Probabilistic Network Latency Verification

### 2023-02-14 paper/main.tex
[Paper] updated various things
[Paper] updated graph for fattree

\documentclass[10pt,sigconf,letterpaper,anonymous,nonacm]{acmart}

@@

\title{Probabilistic Network Latency Verification}
\author{WIP}

@@

\section{Conclusion} \label{sec:conc}
\begin{itemize}
    \item Tempus is a scalable latency SLA verifier. It could probabilistically verify in the order of minutes
    \item Consolidation and memoization is an effective optimization strategy, although the exact magnitude of 
        its effectiveness will depend on the network topology, specifically on the amount of paths and their 
        length.
\end{itemize}

>>>>

\documentclass[10pt,sigconf,letterpaper]{acmart}

@@

\title{Probabilistic Network Latency Verification}
\author{\#929}

@@

\section{Conclusion} \label{sec:conc}
\tool is a scalable latency SLA verifier. 
It could probabilistically verify temporal properties orders of magnitude faster than its unoptimized 
baseline.
Equivalence Class Consolidation and Path Memoization are two effective optimization strategies, 
although the exact magnitude of its effectiveness will depend on the network topology. 
At its best, if the network topology allows only a handful of path between src-dst pair or the paths are 
highly symmetrical, then it could cut temporal verification time up to 6 orders of magnitude.
